formula1

### 2020-06-20 inst/f1points.Rmd
rewording

(observe how this likelihood function, while informative about
$p_4+p_5$, is uninformative about $p_4\left|p_4+p_5\right.$).  We now
use a technique due to \cite{hankin2010,hankin2017} and introduce
fictional (reified) entities whose nonzero Bradley-Terry strength
helps certain competitors or sets of competitors.  The canonical
example would be the home-ground advantage in association football.
If players (teams) $1,2$ with strengths $p_1,p_2$ compete, and if our
observation were $a$ home wins and $b$ away wins for team $1$, and $c$
home wins and $d$ away wins for team $2$, then a suitable likelihood
function would be

@@

```{r, label=calcpoints, echo=FALSE, cache=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points_real <- p
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
m <- maxp(H)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

@@

	goodnesses <- seq_along(pointslist)
	for(i in seq_along(pointslist)){
		p_star <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),pointslist[[i]])
		p_star <- sort(p_star,decreasing=TRUE)
		p_star[] <- seq_along(p_star)
		goodness <- sum(cumprod(names(p_star)==names(l_star)))
		goodnesses[i] <- goodness
		}
	return(goodnesses)
}
pointslist <- list(
	real = points_real,
	top1 = rep(1,1),
	top2 = rep(1,2),
	top3 = rep(1,3),
	top4 = rep(1,4),
	top5 = rep(1,5),
	top6 = rep(1,6),
	top7 = rep(1,7),
	top8 = rep(1,8),
	top9 = rep(1,9),
	topt = rep(1,10),  # effectively punishing the last finisher
   	lin1 = 1,   # same as top1
	lin2 = 2:1,
	lin3 = 3:1,
	lin4 = 4:1,
	lin5 = 5:1,
	lin6 = 6:1,
	lin7 = 7:1,
	lin8 = 8:1,
	lin9 = 9:1,
	lint = 10:1,
	line = 11:1,
	zipf = 1/seq_len(top),
	expa = 1/1.01^seq_len(top),
	expb = 1/1.10^seq_len(top),
	expc = 1/1.20^seq_len(top),
	expd = 1/1.50^seq_len(top),
	exp2 = 1/2^seq_len(top),
	exp3 = 1/3^seq_len(top),
	exp4 = 1/4^seq_len(top)
)
```

```{r,label=multiplemontecarloexecute, cache=TRUE,echo=FALSE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
OO <- replicate(1000,resampling_multiple(m,f2017,pointslist=pointslist))
```

>>>>

(observe how this likelihood function, while informative about
$p_4+p_5$, is uninformative about $p_4\left|p_4+p_5\right.$).  We now
use a technique due to \cite{hankin2010,hankin2017} and introduce
fictional (reified) entities whose nonzero Bradley-Terry strength
helps certain competitors or sets of competitors under certain
conditions.  The canonical example would be the home-ground advantage
in association football.  If players (teams) $1,2$ with strengths
$p_1,p_2$ compete, and if our observation were $a$ home wins and $b$
away wins for team $1$, and $c$ home wins and $d$ away wins for team
$2$, then a suitable likelihood function would be

@@

```{r, label=calcpoints, echo=FALSE, cache=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points_real <- p
points_inaugural <- c(8,6,4,3,2)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
m <- maxp(H)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

@@

	goodnesses <- seq_along(pointslist)
	for(i in seq_along(pointslist)){
		p_star <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),pointslist[[i]])
		p_star <- sort(p_star,decreasing=TRUE)
		p_star[] <- seq_along(p_star)
		goodness <- sum(cumprod(names(p_star)==names(l_star)))
		goodnesses[i] <- goodness
		}
	return(goodnesses)
}
pointslist <- list(
	real = points_real,
	inau = points_inaugural,
	top1 = rep(1,1),
	top2 = rep(1,2),
	top3 = rep(1,3),
	top4 = rep(1,4),
	top5 = rep(1,5),
	top6 = rep(1,6),
	top7 = rep(1,7),
	top8 = rep(1,8),
	top9 = rep(1,9),
	topt = rep(1,10),  # effectively punishing the last finisher
   	lin1 = 1,   # same as top1
	lin2 = 2:1,
	lin3 = 3:1,
	lin4 = 4:1,
	lin5 = 5:1,
	lin6 = 6:1,
	lin7 = 7:1,
	lin8 = 8:1,
	lin9 = 9:1,
	lint = 10:1,
	line = 11:1,
	zipf = 1/seq_len(top),
	expa = 1/1.01^seq_len(top),
	expb = 1/1.10^seq_len(top),
	expc = 1/1.20^seq_len(top),
	expd = 1/1.50^seq_len(top),
	exp2 = 1/2^seq_len(top),
	exp3 = 1/3^seq_len(top),
	exp4 = 1/4^seq_len(top),
	fis1 = c(1,1,1),
	fis2 = c(1,1,0.9),
	fis3 = c(1,1,1,0.1),
	fis4 = c(1,1,0.9,0.1),
	fis5 = c(1,1,0.5),
	fis6 = c(1,1,1,0.5),
	fis7 = c(1,1,0.5,0.5)
)
```

```{r,label=multiplemontecarloexecute, cache=TRUE,echo=FALSE}
set.seed(9)
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
OO <- replicate(1000,resampling_multiple(m,f2017,pointslist=pointslist))
```
